An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-04 EconGrowth2.Rnw
Added LINEX resample plot.

**** Include LINEX scatter graphs here. Cover all 
quantifications of energy? CIs? TBD which to include. ****

>>>>

Figure~\ref{fig:LINEXq_Resample_Graph}
shows the coefficients estimated from resampled data.

<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with energy) resampling results.">>=
# linexResamplePlot(energyType="Q")
linexResamplePlot(energyType="Q")
@
